Reconstructing Propositional Proofs in Type Theory

### 2017-10-23 paper/sections/proof-reconstruction/strip.tex
[ paper ] fixed subgoal description.

In (\ref{eq:strip-example}), by proving each subgoal from left to right in the right conjunction,
we get a proof for the conjecture by using the elimination of the implication .
\end{myexample}

@@

\begin{mainlemma}
  \label{lem:inv-uh-lem}
Let $\text{n} : \Nat$ be the complexity measure of the $\fuh_0$ function
in~(\ref{eq:uh-structured}).
If $Γ ⊢ \fuh₁~φ~n$ then $Γ ⊢ φ$.
\end{mainlemma}

\begin{proof}
The proof is by induction on the cases defined by the outcome of the
$\fuh_{1}$ function in~(\ref{eq:uh-structured}).
\begin{itemize}
  \item If $n = 0$, by definition in~(\ref{eq:uh-structured})
        we conclude $Γ ⊢ φ$.
  \item If $n = 1$, we apply the following theorem proved in~\cite{AgdaProp},
    \begin{equation*}
    \texttt{∧⇒\rm{-to-}⇒⇒}\ :\  Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃ → Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃).
    \end{equation*}
  \item For $n > 1$, we use induction on the structure of the second
        argument.
\vskip 2mm
\begin{itemize}

>>>>

\Metis proves each subgoal in the same order above from left to right
in (\ref{eq:strip-example}).
Besides the fact \Metis does not explicit in \TSTP derivation
how it uses the proofs of subgoals, we know using the elimination
of the implication, we get the proof of the conjecture.
\end{myexample}

@@

\begin{mainlemma}
  \label{lem:inv-uh-lem}
Let $\text{n} : \Nat$ be the complexity measure of the $\fuh_0$ function
in~(\ref{eq:uh-definition}).
If $Γ ⊢ \fuh₁~φ~n$ then $Γ ⊢ φ$, where $\fuh₁$ is the function defined
in (\ref{eq:uh-structured}).
\end{mainlemma}

\begin{proof}
The proof is by induction on the cases defined by the outcome of the
$\fuh_{1}$ function.
\begin{itemize}
  \item If $n = 0$, by definition in~(\ref{eq:uh-structured})
        we conclude $Γ ⊢ φ$.
  \item If $n = 1$, we apply the following theorem proved in~\cite{AgdaProp},
    \begin{equation*}
    \texttt{∧⇒\rm{-to-}⇒⇒}\ :\  Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃ → Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃).
    \end{equation*}
  \item For $n > 1$, we use induction on the structure of the second
        argument.
\vskip 2mm
\begin{itemize}
